{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-26 draft.tex
Revised the abstract.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
application of embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made. However, to successfully deploy
a computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy some criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and executable size. This criteria assumes the performance of the
algorithm is reasonably good. To this end, in this paper, we propose an
ensemble of the kernelized correlation filters (KCF), aka {\it E}nKCF,
for a single-target object tracking. In particular, we developed a
committee of KCFs to specifically address the scale-change and the
translation over frames. In addition, we devised a Bayes filter to
minimize the gap of interactions between KCFs. It is well known that
an online, model-free tracker like ours is prone to drift over
time. To cope with such drifts, we developed a re-detection module
that reliably identifies when to lose the target, hand-picks a small
number of object proposals from existing object proposal methods
(e.g., ``Edge Box''), and re-initializes the track to track the object
for a longer period. To verify the usefulness of the proposed method,
we compared the performance of ours to those of existing online
tracking methods. Experimental results showed that the performance of
ours are precision on 20 pixels, 72.53\%, AUC 52.90\% for OTB100 data
and 55.71\% and 41.71\% for UAV123 data. This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $15\%$-$20\%$ in AUC. Finally,  our implementation ran at 340 fps for OTB100 dataset and at 416 fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($300$ fps) for UAV123.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition on
execution of individual KCFs. To minimize the effect of drifting, we
developed a re-detection module that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
69.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 3\% on AUC on average. Our implementation
ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
faster than DCF (292 fps) for OTB100.
\end{abstract}
